Dynamical modeling of tidal streams

### 2014-01-06 tex/ms.tex
streams: edit

The generative model for a tidal stream proposed here also connects
the dynamics of the stream, in particular its average track and the
dispersion around this track, to the properties of the
progenitor. Primarily, we can constrain $\sigv$, which is proportional
to the velocity dispersion or mass$^{1/3}$ of the progenitor (see
\citealt{Sanders13a}), from the observed width of the stream, even if
the stream's sky projection is the only projection for which we can
resolve the stream. Further $N$-body simulations are necessary to
characterize the exact relation between the \sigv\ parameter and the
velocity dispersion of the progenitor.

>>>>

The generative model for a tidal stream proposed here also connects
the dynamics of the stream, in particular its average track and the
dispersion around this track, to the properties of the
progenitor. Primarily, we can constrain $\sigv$, which is proportional
to the velocity dispersion or mass$^{1/3}$ of the progenitor (see
\citealt{Sanders13a}), from the observed width of the stream, even if
the stream's sky projection is the only projection for which we can
resolve the stream. Further $N$-body simulations are necessary to
characterize the exact relation between the \sigv\ parameter and the
velocity dispersion of the progenitor and to determine the importance
of the cluster's internal structure, primarily its concentration, in
determining \sigv.
